MLCommons Earthquake Science Benchmark

### 2022-02-19 paper-capstone-earthquake.tex
bio images
finish bio image
todo added
fix latex syntax error

@@

\newcommand{\GITISSUE}[1]{\href{https://github.com/Data-ScienceHub/mlcommons-science/issues/#1}{GitHub Issue #1}}}
\newcommand{\GITPULL}[1]{\href{https://github.com/laszewsk/mlcommons/pull/#1}{GitHub Pull #1}}}

@@

\newcommand{\BIOFIG}[3]{%

  {\bf #2} #3
  %\begin{wrapfigure}[l]{.2\columnwidth}
  \includegraphics[width=.2\columnwidth]{#1}%
  %\end{wrapfigure}
}

@@

\BIOFIG{images/bio/gregor.png}{Geoffrey C. Fox}{TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD}

@@

>>>>

\newcommand{\BIOFIG}[3]{%
\parindent 0pt%
\setlength{\intextsep}{6pt}%
\setlength{\columnsep}{6pt}%

{\bf #2}

\begin{wrapfigure}{r}{0.2\columnwidth}%
    \includegraphics[width=0.2\columnwidth]{#1}%
\end{wrapfigure}%
#3%
}

@@

\newcommand{\GITISSUE}[1]{\href{https://github.com/Data-ScienceHub/mlcommons-science/issues/#1}{GitHub Issue #1}}
\newcommand{\GITPULL}[1]{\href{https://github.com/laszewsk/mlcommons/pull/#1}{GitHub Pull #1}}

@@

@@

\BIOFIG{images/bio/fox.png}{Geoffrey C. Fox}{TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD TBD
  TBD TBD TBD TBD TBD TBD TBD TBD}

@@

\TODO{There are more we developed in the web page}
